---
output:
  md_document:
    variant: markdown_github
---


# Overview

## Description

**'recruitR'**: A R package including useful functions for tree
recruitment analyses.

At this stage, I have simply I picked up 5 common seeds dispersal kernel in which all are isotropic:

1. Nathan, R., Klein, E., Robledo-Arnuncio, J. J. & Revilla, E. in Dispersal Ecology and Evolution 186–210 (Oxford University Press, 2012). [doi:10.1093/acprof:oso/9780199608898.003.0015](https://doi.org/10.1093/acprof:oso/9780199608898.003.0015 )




```{r echo=FALSE}
knitr::opts_chunk$set(
  fig.path = "inst/",
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width=4,
  fig.height=4
)
devtools::load_all(".")
```

## Current statut

Last 'README' update: `r format(Sys.time(), '%Y-%m-%d')`

[![Travis](https://travis-ci.org/KevCaz/recruitR.svg?branch=master)](https://travis-ci.org/KevCaz/recruitR)
[![Build status](https://ci.appveyor.com/api/projects/status/sk3sbvusvcyy0at0?svg=true)](https://ci.appveyor.com/project/KevCaz/recruitr/build/1.0.7)
[![codecov](https://codecov.io/gh/KevCaz/recruitR/branch/master/graphs/badge.svg)](https://codecov.io/gh/KevCaz/recruitR)




# Using the package

## Installation

To get the current development version from Github using R, use the
[*devtools*](http://cran.r-project.org/web/packages/devtools/index.html) package:

```r
if (!require("devtools'")) install.packages("devtools")
devtools::install_github("KevCaz/recruitR")
library(recruitR)
```


## Examples

### Using a kernel

A simple call to one on the kernel:

```{r}
kern_gaussian(4, 3)
```

Simple plots:

1. Gaussian kernel:

```{r,  fig.width=6,  fig.height=6}
seqx <- seq(0,10,0.001)
plot(seqx, kern_gaussian(seqx, .5), type='l')
```

2. Log_normal kernel:
```{r,  fig.width=6,  fig.height=6}
plot(seqx, kern_lognormal(seqx, 3, .2), type='l')
```

3. Exponential_powerl kernel:
```{r,  fig.width=6,  fig.height=6}
plot(seqx, kern_exponential_power(seqx,2,3), type='l')
```
