---
title: "Get started with diskers"
author: "Kevin Cazelles"
date: 02-01-2018
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with rcites}
  %\VignetteEngine{knitr::rmarkdown}
---


```{r setup, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  purl = NOT_CRAN,
  eval = NOT_CRAN,
  fig.align = "center",
  comment = "#> "
)
library(diskers)
```


# Kernels

There are five kernels currently available, use `kernels()` to list them:

```{r listkernels}
kernels()
```

First parameter is the distance at which the kernel density is evaluated,
second is the scale parameter and the third is the shape parameter (for kernels that requires 3 parameters):

```{r, results = 'hold'}
kern_gaussian(4, 3)
kern_exponential(4, 3)
#
kern_2Dt(4, 3, 2)
kern_exponential_power(4, 3, 2)
kern_lognormal(4, 3, 2)
```

# Mean dispersal distance

`meanDispDist()` return the mean dispersal distance:

```{r, results = 'hold'}
meanDispDist('gaussian', 3)
meanDispDist('exponential', 3)
meanDispDist('lognormal', 3, 2)
meanDispDist('k2Dt', 3, 2)
meanDispDist('exponential_power', 3, 2)
meanDispDist('lognormal', 3, 2)
```


# Figures

Below, we exemplify how to plot dispersal isotropic kernels with `diskers`.

## Gaussian kernel

```{r, fig.width = 6, fig.height = 6}
seqx <- seq(0, 10, 0.001)
par(las = 1, bty = 'L')
plot(seqx, kern_gaussian(seqx, .5), type='l', lwd=2, col='#0366d6', xlab='Distance', ylab='Density')
```

## Log_normal kernel

```{r,  fig.width = 6,  fig.height = 6}
par(las = 1, bty = 'l')
plot(seqx, kern_lognormal(seqx, 3, .2), type='l', lwd=2, col='#0366d6', xlab='Distance', ylab='Density')
```

## Exponential_power kernel

```{r, fig.width = 6, fig.height = 6}
par(las = 1, bty = 'l')
plot(seqx, kern_exponential_power(seqx,2,3), type='l', lwd=2, col='#0366d6', xlab='Distance', ylab='Density')
```


## References

1. Nathan, R., Klein, E., Robledo-Arnuncio, J. J. & Revilla, E. in Dispersal
Ecology and Evolution 186–210 (Oxford University Press, 2012) -- [doi:10.1093/acprof:oso/9780199608898.003.0015](https://doi.org/10.1093/acprof:oso/9780199608898.003.0015).
